Causal Forest Approach for Site-specific Input Management via On-farm Precision Experimentation

### 2022-02-07 Codes/PrepareResults.rmd
update font type and figure of field structure

# --- figure making --- #
library(RColorBrewer)
library(patchwork)
library(ggplot2)
library(ggthemes)
library(viridis)
library(ggpubr)
library(gridExtra)
library(DiagrammeR)

@@

@@

```{r}
variogram_tb <-
  data.frame(
    Parameters = c("ymax_ij", "alpha_ij", "beta_ij", "varepsilon_ij"),
    Range = c(400, 400, 400, 400),
    Mean = c(12000, -0.5, format(c(0, 0))),
    Nugget = format(c(0, 0, 0, 0)),
    Sill = c(2000000, 0.02, format(1, nsmall = 1), 0.015)
  ) %>%
  flextable() %>%
  compose(i = 1, j = 1, part = "body", value = as_paragraph(as_i("ymax"), as_sup(as_i("i,j")))) %>%
  compose(i = 2, j = 1, part = "body", value = as_paragraph(as_i("\U03B1"), as_sup(as_i("i,j")))) %>%
  compose(i = 3, j = 1, part = "body", value = as_paragraph(as_i("\U03B2"), as_sup(as_i("i,j")))) %>%
  compose(i = 4, j = 1, part = "body", value = as_paragraph(as_i("\U03B5"), as_sup(as_i("i,j")))) %>%
  compose(i = 1, j = 3, part = "body", value = as_paragraph("1.2", "\U2A2F", "10", as_sup("4"))) %>%
  compose(i = 1, j = 5, part = "body", value = as_paragraph("2.0", "\U2A2F", "10", as_sup("6"))) %>%
  compose(i = 1, j = 3, part = "body", value = as_paragraph("1.2", "\U2A2F", "10", as_sup("4"))) %>%
  compose(i = 2, j = 5, part = "body", value = as_paragraph("2.0", "\U2A2F", "10", as_sup("-2"))) %>%
  compose(i = 4, j = 5, part = "body", value = as_paragraph("1.5", "\U2A2F", "10", as_sup("-2"))) %>%
  align(align = "center", part = "all") %>%
  align(j = 1, align = "left", part = "all") %>%
  # --- change headers labels--- #
  set_header_labels(values = list(
    Parameters = "Parameters",
    Range = "Range (m)",
    Mean = "Mean",
    Nugget = "Nugget",
    Sill = "Sill"
  )) %>%
  #- change the borders just for consistency with other tables -#
  hline_bottom(part = "all") %>%
  hline_top(part = "header") %>%
  footnote(
    value = as_paragraph("NOTE: About ymax, the units of of Mean, Nugget, and Sill are kg."),
    ref_symbols = NA
  ) %>%
  autofit()
```

@@

## Division of field: plots, subplots and cells (Visualization)

@@

# == plot-level field without padding area ==##
vis_field_plot <-
  ggplot(field_plot_sf) +
  geom_sf(fill = NA) +
  theme_void() +
  labs(caption = "Bottom Title") +
  theme(plot.title = element_text(hjust = 0.5))

### ==== Example map of plot and subplots and cells ====####
# == Preparation ==##
ex_plot <- field_plot_sf[224, ]
ex_subplots <- field_subplot_sf[ex_plot, , op = st_within]

@@

#-- (1) plot-level field map (base: vis_field_withoutPadding) --#
library(latex2exp)

plot <-
  ggplot() +
  geom_sf(data = field_plot_sf) +
  geom_sf(data = ex_plot, fill = "green", size = 1) +
  # coord_sf(expand = F) +
  theme_void() +
  ggtitle(TeX("$12 \\times 32$ plots")) +
  theme(plot.title = element_text(hjust = 0.5))

@@

# #-- (2) create a map of subplots in a plot --##
subplots_inPlot <- ggplot() +
  geom_sf(data = ex_plot, fill = "green") +
  geom_sf(data = ex_subplots, fill = NA, size = 1) +
  theme_void() +
  ggtitle(TeX("$4 \\times 1$ subplots")) +
  theme(plot.title = element_text(hjust = 0.5))

@@

# #-- (3) create a map of cells in a subplot --#
cells_inSubplot <-
  ggplot() +
  geom_sf(data = ex_one_subplot, fill = "green", size = 1) +
  geom_sf(data = ex_cells, fill = NA) +
  theme_void() +
  ggtitle(TeX("$6 \\times 6$ cells")) +
  theme(
    plot.title = element_text(hjust = 0.5, margin = margin(0, 0, 10, 0))
  )

@@

# #-- (4)put them on the same map --#
g_inset <- ggplot() +
  coord_equal(xlim = c(0, 1), ylim = c(0, 1), expand = FALSE)

map_all_together <-
  # /*----------------------------------*/
  #' ##  base maps
  # /*----------------------------------*/
  g_inset +
  # --- plot level --- #
  annotation_custom(grob_plot,
    xmin = 0, xmax = 0.4, ymin = 0, ymax = 1
  ) +
  # --- subplot level --- #
  annotation_custom(grob_subplots_inPlot,
    xmin = 0.57, xmax = 0.67, ymin = 0.3, ymax = 0.8
  ) + # hight is 5
  # --- cell level --- #
  annotation_custom(grob_cells_inSubplot,
    xmin = 0.8, xmax = 1, ymin = 0.5, ymax = 0.7
  ) +
  # xmin = 0.75, xmax = 1, ymin = 0.45, ymax = 0.7) +
  # /*----------------------------------*/
  #' ## add line segments
  # /*----------------------------------*/
  # --- plot-subplot (above) --- #
  # geom_segment(aes(x = 0.386,  xend = 0.55, y = 0.547, yend = 0.73),
  geom_segment(aes(x = 0.387, xend = 0.57, y = 0.534, yend = 0.717),
    lineend = "round", color = "grey",
    size = 1.5
  ) +
  # --- plot-subplot (below) --- #
  # geom_segment(aes(x = 0.386, xend = 0.55, y = 0.5, yend = 0.37),
  geom_segment(aes(x = 0.387, xend = 0.57, y = 0.485, yend = 0.352),
    # data = arrowA,
    lineend = "round", color = "grey",
    size = 1.5
  ) +
  # --- subplot-cell (above) --- #
  # geom_segment(aes(x = 0.65, xend = 0.805, y = 0.64, yend = 0.692),
  geom_segment(aes(x = 0.671, xend = 0.82, y = 0.626, yend = 0.661),
    # data = arrowA,
    lineend = "round", color = "grey",
    size = 1.5
  ) +
  # --- subplot-cell (below) --- #
  geom_segment(aes(x = 0.671, xend = 0.82, y = 0.532, yend = 0.506),
    # data = arrowA,
    lineend = "round", color = "grey",
    size = 1.5
  ) +
  theme_void()

#     theme(plot.margin=unit(c(0,0,0,0),"mm"))

file <- here("GitControlled/Writing/field_structure.png")
ggsave(file)
knitr::plot_crop(file)
dev.off()
```

@@

```{r}
# /*=================================================*/
#' # Sample CT figure (cach)
# /*=================================================*/

library(causalTree)
library(here)
library(rpart)
library(rattle)

data_sf <- st_read(here("Shared/Data/snider_high_res.gpkg")) %>%
  na.omit() %>%
  dplyr::rename(tgtn = NPlan, tgts = SRPlan)

data_dt <- data.table(data_sf) %>%
  setnames(names(.), tolower(names(.)))

tgts_ls <- data_dt[, tgts] %>%
  unique() %>%
  sort()

ctree_data <- copy(data_dt) %>%
  .[tgts %in% tgts_ls[1:2], ] %>%
  .[, treat := ifelse(tgts == tgts_ls[2], 1, 0)] %>%
  #--- Corn Yield: 1 bu/acre ->  62.77 kg/ha---#
  .[, yield := yield * 62.77]

tree <- causalTree(
  yield ~ slope + ecs,
  data = ctree_data,
  treatment = ctree_data$treat,
  split.Rule = "CT",
  cv.option = "CT",
  split.Honest = T,
  cv.Honest = T,
  split.Bucket = F,
  xval = 5,
  cp = 0,
  minsize = 20,
  propensity = 0.5
)

opcp <- tree$cptable[, 1][which.min(tree$cptable[, 4])]
opfit <- prune(tree, opcp)
```

```{r}
source("./GitControlled/Codes/0_1_functions_gen_analysis_data.R")

pCorn <- price_table[2, pCorn]
pN <- price_table[2, pN]

@@

#/*----------------------------------*/
#' ## (1) cell-level data set 
#/*----------------------------------*/
# + NOTE: I needed to do the following things, because the existing raw data does not have m_error
field <- readRDS(here("Shared/Data/for_Simulations/field_padding.rds"))

coef_data <- readRDS(here("Shared/Data/for_Simulations/coefficients_sprange_400.rds"))

x=1
coef_data_m <- coef_data[sim == x, ]
coef_data_t <- coef_data[sim == ifelse(x + 1 >= max(sim), 1, x + 1), ]

sample_dt_cell <- prepare_raw_data(x, field=field, coef_data_m=coef_data_m, coef_data_t=coef_data_t, app_error="no") %>%
  .$reg_raw_data

field_cell_sf <- 
  left_join(select(field, unique_cell_id), field_cell_dt, by="unique_cell_id")%>%
    na.omit() %>%
    mutate(plot_id = ceiling(subplot_id/4)) %>%
    filter(padding==1)

saveRDS(field_cell_sf, here("Shared/Results/for_writing/sample_field_cell_sf.rds"))

@@

field_subplot_sf <- 
  field_cell_sf %>%
  group_by(subplot_id, strip_id) %>%
  summarise(
    sim = mean(sim),
      yield = mean(yield),
      opt_N = mean(opt_N),
      rate = mean(rate),
      aa_n = mean(aa_n), 
      alpha = mean(alpha),
      beta = mean(beta),
      ymax = mean(ymax),
      alpha1 = mean(alpha1),
      alpha2 = mean(alpha2),
      beta1 = mean(beta1),
      beta2 = mean(beta2),
      ymax1 = mean(ymax1),
      ymax2 = mean(ymax2),
      theta_1 = mean(theta_1),
      theta_2 = mean(theta_2)
  ) %>%
  mutate(unique_subplot_id = paste0(strip_id,"_",subplot_id))%>%
  select(!c(strip_id, subplot_id))

saveRDS(field_subplot_sf, here("Shared/Results/for_writing/sample_field_subplot_sf.rds"))
```

>>>>

# --- figure making --- #
library(ggbrace)
library(RColorBrewer)
library(patchwork)
library(ggplot2)
library(ggthemes)
library(viridis)
library(ggpubr)
library(gridExtra)
library(DiagrammeR)

@@

# figure and table set up

```{r}
theme_update(
  axis.title.x =
    element_text(
      size = 12, angle = 0, hjust = .5, vjust = -0.3, face = "plain", family = "Cambria"
    ),
  axis.title.y =
    element_text(
      size = 12, angle = 90, hjust = .5, vjust = .9, face = "plain", family = "Cambria"
    ),
  axis.text.x =
    element_text(
      size = 10, angle = 0, hjust = .5, vjust = 1.5, face = "plain", family = "Cambria"
    ),
  axis.text.y =
    element_text(
      size = 10, angle = 0, hjust = 1, vjust = 0, face = "plain", family = "Cambria"
    ),
  axis.ticks =
    element_line(
      size = 0.3, linetype = "solid"
    ),
  axis.ticks.length = unit(.15, "cm"),
  #--- legend ---#
  legend.text =
    element_text(
      size = 10, angle = 0, hjust = 0, vjust = 0, face = "plain", family = "Cambria"
    ),
  legend.title =
    element_text(
      size = 10, angle = 0, hjust = 0, vjust = 0, face = "plain", family = "Cambria"
    ),
  legend.key.size = unit(0.5, "cm"),
  #--- strip (for faceting) ---#
  strip.text = element_text(size = 10),
  #--- plot title ---#
  plot.title = element_text(family = "Times", face = "bold", size = 12),
  #--- margin ---#
  # plot.margin = margin(0, 0, 0, 0, "cm"),
  #--- panel ---#
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  panel.background = element_blank(),
  panel.border = element_rect(fill = NA)
)

set_flextable_defaults(
  font.family = "Cambria"
  )
```

@@

```{r}
variogram_tb <-
  data.frame(
    Parameters = c("ymax_ij", "alpha_ij", "beta_ij", "varepsilon_ij"),
    Range = c(400, 400, 400, 400),
    Mean = c(12000, -0.5, format(c(0, 0))),
    Nugget = format(c(0, 0, 0, 0)),
    Sill = c(2000000, 0.02, format(1, nsmall = 1), 0.015)
  ) %>%
  flextable() %>%
  compose(i = 1, j = 1, part = "body", value = as_paragraph(as_i("ymax"), as_sup(as_i("i,j")))) %>%
  compose(i = 2, j = 1, part = "body", value = as_paragraph(as_i("\U03B1"), as_sup(as_i("i,j")))) %>%
  compose(i = 3, j = 1, part = "body", value = as_paragraph(as_i("\U03B2"), as_sup(as_i("i,j")))) %>%
  compose(i = 4, j = 1, part = "body", value = as_paragraph(as_i("\U03B5"), as_sup(as_i("i,j")))) %>%
  compose(i = 1, j = 3, part = "body", value = as_paragraph("1.2", "\U2A2F", "10", as_sup("4"))) %>%
  compose(i = 1, j = 5, part = "body", value = as_paragraph("2.0", "\U2A2F", "10", as_sup("6"))) %>%
  compose(i = 1, j = 3, part = "body", value = as_paragraph("1.2", "\U2A2F", "10", as_sup("4"))) %>%
  compose(i = 2, j = 5, part = "body", value = as_paragraph("2.0", "\U2A2F", "10", as_sup("-2"))) %>%
  compose(i = 4, j = 5, part = "body", value = as_paragraph("1.5", "\U2A2F", "10", as_sup("-2"))) %>%
  align(align = "center", part = "all") %>%
  align(j = 1, align = "left", part = "all") %>%
  # --- change headers labels--- #
  set_header_labels(values = list(
    Parameters = "Parameters",
    Range = "Range (m)",
    Mean = "Mean",
    Nugget = "Nugget",
    Sill = "Sill"
  )) %>%
  #- change the borders just for consistency with other tables -#
  hline_bottom(part = "all") %>%
  hline_top(part = "header") %>%
  footnote(
    value = as_paragraph("NOTE: About ymax, the units of Mean, Nugget, and Sill are kg."),
    ref_symbols = NA
  ) %>%
  autofit()
```

@@

## Division of field: plots, subplots and cells (Visualization)
+ https://stackoverflow.com/questions/35633239/add-curly-braces-to-ggplot2-and-then-use-ggsave

+

@@

# === Preparation === #
ex_plot <- field_plot_sf[224, ]
ex_subplots <- field_subplot_sf[ex_plot, , op = st_within]

@@

one_subplot <- ex_subplots[3,]

#-- (1) plot-level field map  --#
plot <-
  ggplot() +
  geom_sf(data = field_plot_sf) +
  geom_sf(data = ex_plot, fill = "green", size = 1) +
  coord_sf(expand = FALSE) +
  # theme_void() +
  ggtitle(TeX("$12 \\times 32$ plots")) +
  theme(plot.title = element_text(hjust = 0.5))

@@

#-- (2) create a map of subplots in a plot --##
subplots_inPlot <- 
  ggplot() +
  geom_sf(data = ex_plot, fill = "green") +
  geom_sf(data = ex_subplots, fill = NA, size = 1) +
  geom_sf(data = ex_subplots[2,], fill = "skyblue", size = 1) +
  coord_sf(expand = FALSE) +
  theme_void() +
  ggtitle(TeX("$4 \\times 1$ subplots")) +
  theme(plot.title = element_text(hjust = 0.5))

@@

#-- (3) create a map of cells in a subplot --#
cells_inSubplot <-
  ggplot() +
  geom_sf(data = ex_one_subplot, fill = "green", size = 1) +
  geom_sf(data = ex_cells, fill = NA) +
  geom_sf(data = ex_cells[2,], fill = "skyblue", size = 1) +
  coord_sf(expand = FALSE) +
  theme_void() +
  ggtitle(TeX("$6 \\times 6$ cells")) +
    theme(
    plot.title = element_text(hjust = 0.5)
  )

@@

#-- (4)put them on the same map --#
field_structure <-
  ggplot() +
  coord_equal(xlim = c(0, 1), ylim = c(0, 1), expand = FALSE)+
  # /*----------------------------------*/
  #' ##  base maps
  # /*----------------------------------*/
  # --- plot level --- #
  annotation_custom(grob_plot,
    xmin = 0, xmax = 0.4, ymin = 0, ymax = 1) +
  # --- subplot level --- #
  annotation_custom(grob_subplots_inPlot,
    xmin = 0.565, xmax = 0.665, ymin = 0.35, ymax = 0.7) + 
  # --- cell level --- #
  annotation_custom(grob_cells_inSubplot,
    xmin = 0.8, xmax = 0.8+0.2, ymin = 0.382, ymax = 0.382 +0.2) +
  #/*----------------------------------*/
  #' ## Add braces
  #/*----------------------------------*/
  # --- between plot and subplot --- #
  geom_brace(aes(c(0.43,0.43+0.1), c(0.353, 0.661)), color ="red", rotate = 270, inherit.data=F) +
  # --- between subplot and cell --- #
  geom_brace(aes(c(0.68, 0.68 + 0.1), c(0.381, 0.549)), color ="red", rotate = 270, inherit.data=F) +
  #/*----------------------------------*/
  #' ## add annotations
  #/*----------------------------------*/
  # --- annotation for plot --- #
  geom_segment(aes(x = 0.42, xend = 0.393, y = 0.60, yend = 0.515),
    arrow = arrow(length = unit(0.1, "cm")), size=0.5) +
  annotate("text", x = 0.42 + 0.015, y = 0.60 + 0.015, label = "plot") +
  # --- annotation for subplot --- #
  geom_segment(aes(x = 0.7, xend = 0.64, y = 0.37, yend = 0.45),
    arrow = arrow(length = unit(0.1, "cm")), size=0.5) +
  annotate("text", x = 0.7 + 0.035, y = 0.37 - 0.01, label = "subplot") +
  # --- annotation for cell --- #
  geom_segment(aes(x = 0.89, xend = 0.86, y = 0.349, yend = 0.394),
    arrow = arrow(length = unit(0.1, "cm")), size=0.5) +
  annotate("text", x = 0.89 + 0.015, y = 0.349 - 0.01, label = "cell") +
  # coord_sf(expand = FALSE) +
  theme_void() 
```

@@

# Create

```{r, cache = TRUE}
# /*=================================================*/
#' # Sample CT figure 
# /*=================================================*/

library(causalTree)
library(rattle)

data_sf <- st_read(here("Shared/Data/snider_high_res.gpkg")) %>%
    na.omit() %>%
    dplyr::rename(tgtn=NPlan,tgts=SRPlan)

data_dt <- data.table(data_sf) %>%
    setnames(names(.),tolower(names(.)))

tgts_ls <- data_dt[,tgts] %>% unique() %>% sort

ctree_data <- copy(data_dt) %>%
  .[tgts %in% tgts_ls[1:2],] %>%
  .[,treat:=ifelse(tgts==tgts_ls[2],1,0)] %>%
  #--- Corn Yield: 1 bu/acre ->  62.77 kg/ha---#
  .[,yield:= yield*62.77]

tree <- causalTree(
  yield ~ slope+ecs,
  data = ctree_data,
  treatment = ctree_data$treat,
  split.Rule = "CT",
  cv.option = "CT",
  split.Honest = T,
  cv.Honest = T,
  split.Bucket = F,
  xval = 5,
  cp = 0,
  minsize = 20,
  propensity = 0.5
)

opcp <- tree$cptable[,1][which.min(tree$cptable[,4])]
opfit <- prune(tree, opcp)

```

# Prepare sample field data set by plot, subplot, and cell resolution (one-time run)

```{r}
# source("./GitControlled/Codes/0_1_functions_gen_analysis_data.R")

# pCorn <- price_table[2, pCorn]
# pN <- price_table[2, pN]

@@

#/*----------------------------------*/
#' ## (1) cell-level data set 
#/*----------------------------------*/
# + NOTE: I needed to do the following things, because the existing raw data does not have m_error
# field <- readRDS(here("Shared/Data/for_Simulations/field_padding.rds"))

# coef_data <- readRDS(here("Shared/Data/for_Simulations/coefficients_sprange_400.rds"))

# x=1
# coef_data_m <- coef_data[sim == x, ]
# coef_data_t <- coef_data[sim == ifelse(x + 1 >= max(sim), 1, x + 1), ]

# sample_dt_cell <- prepare_raw_data(x, field=field, coef_data_m=coef_data_m, coef_data_t=coef_data_t, app_error="no") %>%
#   .$reg_raw_data

# field_cell_sf <- 
#   left_join(select(field, unique_cell_id), field_cell_dt, by="unique_cell_id")%>%
#     na.omit() %>%
#     mutate(plot_id = ceiling(subplot_id/4)) %>%
#     filter(padding==1)

# saveRDS(field_cell_sf, here("Shared/Results/for_writing/sample_field_cell_sf.rds"))

@@

# field_subplot_sf <- 
#   field_cell_sf %>%
#   group_by(subplot_id, strip_id) %>%
#   summarise(
#     sim = mean(sim),
#       yield = mean(yield),
#       opt_N = mean(opt_N),
#       rate = mean(rate),
#       aa_n = mean(aa_n), 
#       alpha = mean(alpha),
#       beta = mean(beta),
#       ymax = mean(ymax),
#       alpha1 = mean(alpha1),
#       alpha2 = mean(alpha2),
#       beta1 = mean(beta1),
#       beta2 = mean(beta2),
#       ymax1 = mean(ymax1),
#       ymax2 = mean(ymax2),
#       theta_1 = mean(theta_1),
#       theta_2 = mean(theta_2)
#   ) %>%
#   mutate(unique_subplot_id = paste0(strip_id,"_",subplot_id))%>%
#   select(!c(strip_id, subplot_id))

# saveRDS(field_subplot_sf, here("Shared/Results/for_writing/sample_field_subplot_sf.rds"))

#/*----------------------------------*/
#' ## (3) plot-level dataset without padding area  
#/*----------------------------------*/
# field_plot_sf <- field_cell_sf%>%
#     group_by(plot_id, strip_id, rate)%>%
#     summarise()

# saveRDS(field_plot_sf, here("Shared/Results/for_writing/sample_field_plot_sf.rds"))
```

### 2022-02-07 Writing/manuscript_cea.rmd
update font type and figure of field structure

```{r field-map, out.width="50%", fig.cap = "Partitioning of field into plots, subplots and cells"}
# knitr::include_graphics("./GitControlled/Writing/field_structure.png")
readPNG(here("GitControlled/Writing/field_structure.png")) %>% grid.raster()
```

@@

```{r ct-ex, fig.width=4, fig.height=4, fig.align="center", fig.cap = "An illustrative example of causal tree"}
fancyRpartPlot(opfit, sub = "")
```

>>>>

```{r field-map, fig.width=8, fig.height=8, fig.cap = "Partitioning of field into plots, subplots and cells"}
field_structure
```

@@

```{r ct-ex, fig.width=4, fig.height=4, fig.align="center", fig.cap = "An illustrative example of causal tree"}
fancyRpartPlot(opfit,sub='')
```
